---
title: "Cabbages"
author: "Elizabeth Rivera"
date: "07-SEP-2022"
output:
  html_document:
    df_print: paged
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
require(MASS)
veggy <- cabbages
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->
 The cabbages data from the MASS package is loaded into a dataframe called veggy. Complete this report by answering the following two questions  
 
### Is there a difference in average VitC between c39 and c52 cultivation methods?  

$H_0$: There is no difference between the average VitC between C39 and C52.  
$H_A$: The alternative is there is a significant difference between the average VitC between C39 and C52.

# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->

The response variable is 'how much vitC' it is numerical  
The explanatory variable is which cultivation method, it is categorical. We use a numerical to get a categorical. 

# Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
boxplot(VitC~Cult,data=veggy)
```

This box plot shows C52  produces more VitC than C39. The 75th percentile of C52 is 70 and the 25th percentile is about 58. The 75th percentile of C39 is 55 and the 25th percentile is 45. 

### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
favstats(VitC~Cult,data=veggy)
```

This table shows that the median value of VitC for C52 is 64.5 which is greater than C39 with a value of 51.0. The mean of C39 is 51.5 and the mean of C52 is 64.4 demonstrating C52 has a greater VitC value than C39.

## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfies the assumptions and is appropriate to answer the research question!-->

```{r}
t.test(VitC~Cult,data=veggy)
```

The p-value is 0.00000003405 is less than 0.5; so we reject the null hypothesis. 

# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variables causes the other, or whether they perhaps are related for some other reason.  Watch the chapter 6 videos from the George Town videos collection.!-->


The p-value was 0.00000003405 is less than 0.5; we reject the null hypothesis. There is a significant difference between concentrations of VitC  C39 and C52. C52 has a significantly greater concentration cultivation than C39 based on the graphs/ data above. 